Designing for Multiple Use and At-Risk Users: Tor Configuration Launcher

### 2016-03-29 pets2017-paper/pets2017-paper.tex
qualitative recruitment section

\subsubsection{Recruitment}

\subsubsection{Procedure}
We conducted a qualitative evaluation of the interface by creating an environment 
for users to interact with the configuration interface in a censored environment, 
observing their interactions in real time without interacting with the participants, 
and following up with interviews about their experiences.
Using established best practices from the field of user experience research
(\cite{howmanyusers}), we recruited five users for each censorship environment.
We pre-screened our participants to have a good mix of gender, age, technical
background, and familiarity with Tor in each environment.

@@

The 1-hour, single-participant procedure begins when a participant enters a small 
room with a single computer, which is equipped with Chrome, Firefox, Internet Explorer, 
Chrome, and VLC (for screen recording). A participant is firstly informed of 
the risks of the study and consenting to data collection. If they consent, the 
experiment begins. The participant is informed that they are in a
simulated censorship environment, where some websites are blocked. We
instruct them to visit a sample blocked website and a sample non-blocked website on a
non-Tor browser of their choice to illustrate the situation.

>>>>

\subsubsection{Recruitment}
Using established best practices from the field of user experience research
(\cite{howmanyusers}), we recruited 5 participants for each censorship environment.
We pre-screened our participants for diversity of gender, age, technical expertise,
and familiarity with Tor in each simluated censorship environment.

We recruited our users from Craigslist. The recruitment text can be found in 
Appendix \ref{qualitative-recruitment}. The recruitment posting contained a 
SurveyGizmo online survey that collected information about our participants.
The complete prescreening survey can be found in Appendix \ref{qualitative-prescreening}.

We chose our participants based on the pre-screening information to have 
at least one person who has never heard of Tor, at least one person who has 
only heard of Tor, and exactly one person who has previously used Tor in each
environment. We also tried to evenly distribute any participants who had technical
expertise or used particular security tools throughout the censorship environments.

Out of our 16 participants, ages ranged from {\color {red} TODO}
(sigma = {\color {red} TODO}). {\color {red} TODO} of our participants had at least
a college education, and the most common jobs included {\color {red} TODO} and
{\color {red} TODO}. {\color {red} TODO} had heard of Tor previously, 
and {\color {red} TODO} had used Tor previously. {\color {red} TODO} out of 
16 did not use any circumvention tools, and no more than {\color {red} TODO} 
knew any more than {\color {red} TODO} technological terms.

@@

\subsubsection{Procedure}
We conducted a qualitative evaluation of the interface by creating an environment 
for users to interact with the configuration interface in a censored environment, 
observing their interactions in real time without interacting with the participants, 
and following up with interviews about their experiences.

The 1-hour, single-participant procedure begins when a participant enters a small 
room with a single computer, which is equipped with Tor, Chrome, Firefox, Internet Explorer, 
Chrome, and VLC (for screen recording). A participant is firstly informed of 
the risks of the study and consenting to data collection. If they consent, the 
experiment begins. A researcher informs the participant that they are in a
simulated censorship environment, where some websites and services are blocked. 
For the full script of what participants have heard, see Appendix \ref{qualitative-script}. We
instruct them to visit a sample blocked website and a sample non-blocked website on a
non-Tor browser of their choice to illustrate the situation.
